Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-14 csf-2017/paper.tex
removed comment

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
\lau{Do we want to use the term ``pointer'' at any point? I have also used it, but I guess it might create some confusing to whether we have traditional pointer as well as capabilities?}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a stack and return pointer
management scheme that enforces control flow integrity in a way that is provably
watertight, potentially efficient, does not rely on a trusted central stack
manager, and with support for exposing higher-order interfaces to an adversary.
In this section, we explain this discipline. We start by explaining the
high-level approach, the different issues that need to be taken into account,
starting with first-order interfaces and moving onto a higher-order setting
after that. After that, we define a number of reusable macro-instructions that
can be used to conveniently apply the proposed discipline in subsequent
examples.

>>>>

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
%\lau{Do we want to use the term ``pointer'' at any point? I have also used it, but I guess it might create some confusing to whether we have traditional pointer as well as capabilities?}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a stack and return pointer
management scheme that enforces control flow integrity in a way that is provably
watertight, potentially efficient, does not rely on a trusted central stack
manager, and with support for exposing higher-order interfaces to an adversary.
In this section, we explain this discipline. We start by explaining the
high-level approach, the different issues that need to be taken into account,
starting with first-order interfaces and moving onto a higher-order setting
after that. After that, we define a number of reusable macro-instructions that
can be used to conveniently apply the proposed discipline in subsequent
examples.
